---
title: "hw_10"
author: "Merly Klaas"
date: "11/30/2021"
output: 
    html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      highlight: zenburn
      code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(ggthemes)
library(forcats)
library(knitr)
library(kableExtra)
library(gt)
```


# 2a. Reorder factors
  * Get familiar with the gss_cat data within the {forcats} package.
  * Remove the rows with missing data in the tvhours column
  * Calculate the mean tvhours by marital status.
  * Display the results as a point plot of average TV consumption by marital status (tvhours on the x-axis and martial on they y-axis)
  * In your plot, reorder the levels of marital according to tvhours. 
  * Give your plot meaningful axis labels and a title.

```{r}
summary <- gss_cat %>% 
  filter(!is.na(tvhours)) %>% 
  group_by(marital) %>% 
  summarise(tvhours_mean = mean(tvhours, na.rm = TRUE)) %>% 
  mutate(marital = fct_reorder(marital, tvhours_mean))
  
summary %>% ggplot(aes(tvhours_mean, marital)) +
  geom_point() +
    labs(title = "Table 1",
         subtitle = "TV Consumption by Marital Status", 
         x = "The Average TV Hours", 
         y = "Marital Status")

```

# 2b. Working with tables
  * Display the same results (mean tvhours by marital status) as a table using kable().
  * Change the column names.
  * Round the mean tvhours to one decimal.
  * Bold the row with the highest mean tvhours.

```{r}
gss_cat %>% 
  filter(!is.na(tvhours)) %>% 
  group_by(marital) %>% 
  summarise(tvhours_mean = mean(tvhours, na.rm = TRUE)) %>% 
  mutate(marital = fct_reorder(marital, tvhours_mean)) %>% 
  arrange(tvhours_mean) %>% 
  kable(
    col.names = c("Marital Status", "Average TV Hours"),
    digits = 1) %>% 
    row_spec(6, bold = TRUE)
```
# 3a. Recode factors
  * Use any of the functions we talked about in class to display the levels of the marital variable. 
  * Recode or collapse the marital column into three categories: “Not married”, “Married”, and “No answer”.
  * Calculate the mean tvhours by marital status.
  * Display the results as a column plot of average TV consumption by marital status (martial on the x-axis and tvhours on they y-axis).
  * From left to right, the columns in your plot should read: “Not married”, “Married”, and “No answer”.
  * Make your plot look a little nicer with some color, different theme, meaningful axis labels, and a title.
  
```{r}
levels(gss_cat$marital)
gss_cat %>% 
  drop_na() %>% 
  mutate(marital = fct_collapse(marital,
                                `Not married` = c("Never married", "Separated", "Divorced", "Widowed"),
                                Married = c("Married"),
                                `No Answer` = c("No Answer"))) %>%  
  group_by(marital) %>% 
  summarize(tv_hours_mean = mean(tvhours)) %>% 
  mutate(marital = fct_relevel(marital,
              "Not married",
              "Married",
              "No Answer")) %>% 
  ggplot(aes(marital,tv_hours_mean)) + 
  geom_col(stat ="identity", fill = "#FF9999", color = "red")+
  theme_tufte() +
  scale_fill_manual(values = colorblind_pal()(3)) +
  scale_color_manual(values = colorblind_pal()(3))+
  labs(title = "Average TV Consumption by Collapsed Marital Status",
       subtitle = "Not married, Married, No Answer",
       x = "Marital Status",
       y = "Average TV Hours") 

```

# 3b. Working with tables
  * Display the same results (mean tvhours by collapsed marital status) as a table using the {gt}.
  * Change the column names.
  * Round the mean tvhours to one decimal.
  * Highlight in yellow the row with the lowest mean tvhours.
  
```{r}

gss_cat %>% 
  drop_na() %>% 
  mutate(marital = fct_collapse(marital,
                                `Not married` = c("Never married", "Separated", "Divorced", "Widowed"),
                                Married = c("Married"),
                                `No Answer` = c("No Answer"))) %>%  
  group_by(marital) %>% 
  summarize(tv_hours_mean = mean(tvhours)) %>% 
  arrange(desc(tv_hours_mean)) %>% 
  gt() %>% 
  cols_label(marital = "collapsed_marital_status",
             tv_hours_mean = "average_tvhours") %>% 
  fmt_number(columns = 2,
             decimals = 1) %>% 
  tab_style(
    cell_fill(color = "yellow"),
    locations = (cells_body(
      rows = 3))
    )
```

  
